---
title: "Intro Examples to grizbayr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(grizbayr)
library(dplyr)
```

## About the Package

Bayesian Inference is a method of statistical inference that can be used in the analysis of observed data from marketing tests. Bayesian updates start with a prior distribution (prior probable information about the environment) and a likelihood function (an expected distribution from which the samples are drawn). Then, given some observed data, the prior can be multiplied by the likelihood of the data to produce a posterior distribution of probabilities. At the core of all of this is Bayes' Rule. 

$$ P(A\ |\ Data) \sim P(Data\ |\ A) \cdot P(A)$$
This package is intended to abstract the math of the conjugate prior update rules to provide 3 pieces of information for a user:

1. Win Probability (overall and vs baseline)
1. Value Remaining
1. Lift vs. Control

## Usage

Select which piece of information you would like to calculate.

| Metric                       | Function Call                     |
|------------------------------|-----------------------------------|
| All Below Metrics            | `calculate_all_metrics()`         |
| Win Probability              | `estimate_win_prob()`             |
| Value Remaining              | `estimate_value_remaining()`      |
| Lift vs. Control             | `estimate_lift_vs_baseline()`     |
| Win Probability vs. Baseline | `estimate_win_prob_vs_baseline()` |

If you would like to calculate all the metrics then use `calculate_all_metrics()`. This is a slightly more efficient implementation since it only needs to sample from the posterior once for all 4 calculations instead of once for each metric.

### Create an Input Dataframe or Tibble

All of these functions require a very specific tibble format. However, the same tibble can be used in all metric calculations. A tibble is used here because it has the additional check that all column lengths are the same. A tibble of this format can also conveniently be created using dplyr's `group_by() %>% summarise()` sequence of functions.

The columns in the following table are required if there is an `X` in the box for the distribution. (Int columns can also be dbl due to R coercian)

| Distribution Type         | option_name (char) | sum_impressions (int) | sum_clicks (int) | sum_sessions (int) | sum_conversions (dbl) | sum_revenue (dbl) | sum_cost (dbl) | sum_conversions_2 (dbl) | sum_revenue_2 (dbl) | sum_duration (dbl) | sum_page_views (int) |
|---------------------------|:------------------:|:---------------------:|:----------------:|:------------------:|:---------------------:|:-----------------:|:--------------:|:-----------------------:|:-------------------:|:------------------:|:--------------------:|
| Conversion Rate           |          X         |                       |         X        |                    |           X           |                   |                |                         |                     |                    |                      |
| Response Rate             |          X         |                       |                  |          X         |           X           |                   |                |                         |                     |                    |                      |
| Click Through Rate (CTR)  |          X         |           X           |         X        |                    |                       |                   |                |                         |                     |                    |                      |
| Revenue Per Session       |          X         |                       |                  |          X         |           X           |         X         |                |                         |                     |                    |                      |
| Multi Revenue Per Session |          X         |                       |                  |          X         |           X           |         X         |                |             X           |           X         |                    |                      |
| Cost Per Activation (CPA) |          X         |                       |         X        |                    |           X           |                   |        X       |                         |                     |                    |                      |
| Total CM                  |          X         |           X           |         X        |                    |           X           |         X         |        X       |                         |                     |                    |                      |
| CM Per Click              |          X         |                       |         X        |                    |           X           |         X         |        X       |                         |                     |                    |                      |
| Cost Per Click (CPC)      |          X         |                       |         X        |                    |                       |                   |        X       |                         |                     |                    |                      |
| Session Duration          |          X         |                       |                  |          X         |                       |                   |                |                         |                     |           X        |                      |
| Page Views Per Session    |          X         |                       |                  |          X         |                       |                   |                |                         |                     |                    |            X         |

#### Example:
We will use the Conversion Rate distribution for this example so we need the columns **option_name**, **sum_clicks**, and **sum_conversions**.

```{r}
raw_data_long_format <- tibble::tribble(
   ~option_name, ~clicks, ~conversions,
            "A",       6,           3,
            "A",       1,           0,
            "B",       2,           1,
            "A",       2,           0,
            "A",       1,           0,
            "B",       5,           2,
            "A",       1,           0,
            "B",       1,           1,
            "B",       1,           0,
            "A",       3,           1,
            "B",       1,           0,
            "A",       1,           1
)

raw_data_long_format %>% 
  dplyr::group_by(option_name) %>% 
  dplyr::summarise(sum_clicks = sum(clicks), 
                   sum_conversions = sum(conversions))
```

This input dataframe can also be created manually if the aggregations are already done in an external program.

```{r}
# Since this is a stochastic process with a random number generator,
# it is worth setting the seed to get consistent results.
set.seed(1776)

input_df <- tibble::tibble(
  option_name = c("A", "B", "C"),
  sum_clicks = c(1000, 1000, 1000),
  sum_conversions = c(100, 120, 110)
)
input_df
```

One note: clicks or sessions must be greater than or equal to the number of conversions (this is a rate bound between 0 and 1).

`input_df` is used in the following examples. 

### Estimate All Metrics

This function wraps all the below functions into one call.

```{r}
estimate_all_values(input_df, distribution = "conversion_rate", wrt_option_lift = "A")
```


### Win Probability

This produces a tibble with all the option names, the `win_prob_raw` so this can be used as a double, and a cleaned string `win_prob` where the decimal is represented as a percent. 

```{r}
estimate_win_prob(input_df, distribution = "conversion_rate")
```

### Value Remaining (Loss)

Value Remaining is a measure of loss. If B is selected as the current best option, we can estimate with 95% confidence (default), that an alternative option is not more than X% worse than the current expected best option. 

```{r}
estimate_value_remaining(input_df, distribution = "conversion_rate")
```

This number can also be framed in absolute dollar terms (or percentage points in the case of a rate metric).

```{r}
estimate_value_remaining(input_df, distribution = "conversion_rate", metric = "absolute")
```

### Estimate Lift

The `metric` argument defaults to `lift` which produces a percent lift vs the baseline. Sometimes we may want to understand this lift in absolute terms (especially when samples from the posteriors could be negative, such as Contribution Margin (CM).)

```{r}
estimate_lift_vs_baseline(input_df, distribution = "conversion_rate", wrt_option = "A")
```

```{r}
estimate_lift_vs_baseline(input_df, distribution = "conversion_rate", wrt_option = "A", metric = "absolute")
```

### Win Probability vs. Baseline

This function is used to compare an individual option to the best option as opposed to the win probability of each option overall.

```{r}
estimate_win_prob_vs_baseline(input_df, distribution = "conversion_rate", wrt_option = "A")
```

### Sample From the Posterior

Samples can be directly collected from the posterior with the following function.

```{r}
sample_from_posterior(input_df, distribution = "conversion_rate")
```

## Alternate Distribution Type (Rev Per Session)
```{r}
(input_df_rps <- tibble::tibble(
   option_name = c("A", "B", "C"),
   sum_sessions = c(1000, 1000, 1000),
   sum_conversions = c(100, 120, 110),
   sum_revenue = c(900, 1200, 1150)
))

estimate_all_values(input_df_rps, distribution = "rev_per_session", wrt_option_lift = "A")
```



## Valid Posteriors

You may want to pass alternate priors to a distribution. 
Only do this if you are making an informed decision.

```
Beta - alpha0, beta0
Gamma - k0, theta0 (k01, theta01 if alternate Gamma priors are required)
Dirichlet - alpha_00 (none), alpha_01 (first conversion type), alpha_02 (alternate conversion type)
```

```{r}
# You can also pass priors for just the Beta distribution and not the Gamma distribution.
new_priors <- list(alpha0 = 2, beta0 = 10, k0 = 3, theta0 = 10000)
estimate_all_values(input_df_rps, distribution = "rev_per_session", wrt_option_lift = "A", priors = new_priors)
```

## Looping Over All Distributions

You may want to evaluate the results of a test in multiple different distributions.

```{r}
(input_df_all <- tibble::tibble(
   option_name = c("A", "B", "C"),
   sum_impressions = c(10000, 9000, 11000),
   sum_sessions = c(1000, 1000, 1000),
   sum_conversions = c(100, 120, 110),
   sum_revenue = c(900, 1200, 1150),
   sum_cost = c(10, 50, 30),
   sum_conversions_2 = c(10, 8, 20),
   sum_revenue_2 = c(10, 16, 15)
) %>% 
  dplyr::mutate(sum_clicks = sum_sessions)) # Clicks are the same as Sessions

distributions <- c("conversion_rate", "response_rate", "ctr", "rev_per_session", "multi_rev_per_session", "cpa", "total_cm", "cm_per_click", "cpc")

# Purrr map allows us to apply a function to each element of a list. (Similar to a for loop)
purrr::map(distributions,
           ~ estimate_all_values(input_df_all,
                                 distribution = .x,
                                 wrt_option_lift = "A",
                                 metric = "absolute")
)
```

